### 2014-03-12 src/analysis.Rnw
update

\subsection{Sampling Criteria}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())
#myopts <-   theme_bw() +
#  opts(axis.line = theme_segment(colour = "black"),
#    panel.grid.major = theme_blank(),
#    panel.grid.minor = theme_blank(),
#    panel.border = theme_blank(),
#    panel.background = theme_blank())
  #theme with white background
#myopts <- theme_bw() +
  #eliminates background, gridlines, and chart border
#  theme(
#    plot.background = element_blank()
#   ,panel.grid.major = element_blank()
#   ,panel.grid.minor = element_blank()
#   ,panel.border = element_blank()
#  ) +
  #draws x and y axis line
#  theme(axis.line = element_line(color = 'black'))
#myopts <-  opts() #theme_classic()
#+ opts(strip.background = theme_rect(colour = 'NA', fill = 'NA')) + opts(strip.text.y = theme_text(colour = 'white')) + theme(axis.line = element_line(color = 'black'))

# TODO - replace by o.processed.
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

\subsubsection{Lines per element}
The aim of this criteria is similar in some sense to selective mutation. While n-selective mutation ignores the most numerous mutant species, this criteria seeks to deprioritize the most complex program elements.

@@

The results of this selection criteria are provided in Table~\ref{tbl:locsel}. The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.

% ----------------------------------------------------------------------
\subsubsection{One per element}
The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.

@@

The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
% ----------------------------------------------------------------------
% <<oth>>=
% stats.o <- subset(stats.rest, !grepl('^op', operator))
% o.stats.sel.o <- subset(o.f(stats.o), select=sel.colnames)
% r.stats.sel.o <- subset(r.f(stats.o), select=sel.colnames)
% stats.rest <- subset(stats.rest, grepl('^op', operator))
% colnames(o.stats.sel.o) <- new.colnames
% colnames(r.stats.sel.o) <- new.colnames
% @
% 
% \begin{table*}
% \begin{minipage}[h]{0.49\linewidth}
% <<results='asis'>>=
% print(xtable(o.stats.sel.o, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
% @
% \end{minipage}
% \hspace{0.5cm}
% \begin{minipage}[h]{0.49\linewidth}
% <<results='asis'>>=
% print(xtable(r.stats.sel.o, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
% @
% \end{minipage}
% \bigskip
% \caption {Others}
% \label{tbl:osel}
% \end{table*}
% 
% ----------------------------------------------------------------------

\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

@@

For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
% The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
% TODO : Check if this makes sense.
%\begin{figure*}[t]
%\includegraphics[totalheight=6cm]{fig/original.pdf}
%\caption{Subsumption Original}
%\label{fig:subsumptiono}
%\end{figure*}

>>>>

%\subsection{Sampling Criteria}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

%\subsubsection{Lines per element}
%The aim of this criteria is similar in some sense to selective mutation. While n-selective mutation ignores the most numerous mutant species, this criteria seeks to deprioritize the most complex program elements.

@@

%The results of this selection criteria are provided in Table~\ref{tbl:locsel}. The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.

% ----------------------------------------------------------------------
%\subsubsection{One per element}
%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.

@@

%The values are given in Table~\ref{tbl:onesel}, and its visaulization is in Figure~\ref{fig:onesel}.
% ----------------------------------------------------------------------
% <<oth>>=
% stats.o <- subset(stats.rest, !grepl('^op', operator))
% o.stats.sel.o <- subset(o.f(stats.o), select=sel.colnames)
% r.stats.sel.o <- subset(r.f(stats.o), select=sel.colnames)
% stats.rest <- subset(stats.rest, grepl('^op', operator))
% colnames(o.stats.sel.o) <- new.colnames
% colnames(r.stats.sel.o) <- new.colnames
% @
% 
% \begin{table*}
% \begin{minipage}[h]{0.49\linewidth}
% <<results='asis'>>=
% print(xtable(o.stats.sel.o, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
% @
% \end{minipage}
% \hspace{0.5cm}
% \begin{minipage}[h]{0.49\linewidth}
% <<results='asis'>>=
% print(xtable(r.stats.sel.o, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
% @
% \end{minipage}
% \bigskip
% \caption {Others}
% \label{tbl:osel}
% \end{table*}
% 
% ----------------------------------------------------------------------

%\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

@@

%For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
% The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
% TODO : Check if this makes sense.
%\begin{figure*}[t]
%\includegraphics[totalheight=6cm]{fig/original.pdf}
%\caption{Subsumption Original}
%\label{fig:subsumptiono}
%\end{figure*}
